# shawnavote

## Introduction

### Data

```{r}
library(readr)
library(ggplot2)

data <- read_csv("data/shawnavoterdata.csv")

head(data)

ggplot(data, aes(x = Year)) +
  geom_bar(fill = "lightgreen")
```

```{r}
ggplot(data, aes(x = Geo_Unit, y = Turnout)) +
  geom_col(fill = "lightblue") +
  labs(
    x = "Assembly District",
    y = "Turnout",
    title = "Voter Turnout by Assembly District"
  )
```

```{r}
head (data)

dim(data)

```

```{r}

library(sf)
library(tigris)
library(ggplot2)
library(dplyr)
```

```{r}
map_data <- ny_assembly |>
  mutate(Geo_Unit = as.character(SLDLST)) |>
  left_join(data, by = "Geo_Unit") |>
  mutate(turnout_group = cut(
    Turnout,
    breaks = c(0, 0.05, 0.1, 0.2, 1),
    labels = c("Very Low", "Low", "Moderate", "High"),
    include.lowest = TRUE
  ))

ggplot(map_data) +
  geom_sf(aes(fill = turnout_group), color = "white") +
  scale_fill_manual(
    values = c(
      "Very Low" = "#E5F5E0",   
      "Low" = "#A1D99B",       
      "Moderate" = "#31A354",  
      "High" = "#00441B"
    ),
    na.value = "lightgrey"
  ) +
  coord_sf(
    xlim = c(-74.3, -73.65),
    ylim = c(40.45, 40.95),
    expand = FALSE
  ) +
  labs(
    title = "NYC Voter Turnout: Missing Data Included",
    fill = "Turnout Level"
  ) +
  theme_minimal()
```

Perceptually uniform?

Indicates that turnout is low to moderate in NYC. High turnout concentrated is sporadic areas of Manhattan and Brooklyn/Queens. Overall, these areas are centralized around the denser populated regions. The outer boroughs are lower in their levels of turnout.

### Data Description

### Missing Value Analysis

```{r}
library(remotes)


library(redav)
plot_missing(mtcars)
```

```{r}
colSums(is.na(data))

```

This can be likely attributed to districts not reporting their data.

```{r}
library(tidyverse)

voterdata <- data |>
  rownames_to_column("id") |>
  pivot_longer(cols = -id,
               values_transform = list(value = as.character)) |>
  mutate(missing = ifelse(is.na(value), "yes", "no"))

ggplot(voterdata, aes(x = name, y = id, fill = missing)) +
  geom_tile() +
  scale_fill_viridis_d() +
  labs(title = "Voter Data with NAs") +
  theme_bw() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())
```

```{r}
library(mi)
library(dplyr)
plot_missing (data, percent = FALSE)
plot_missing (data)
```

### Results

### Conclusion
